---
title: "Challenge 2"
author: "Fernando Astorga"
date: "September 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r load_data}
gapminder <- read.table("../Data/gapminder.txt")
gapminder

# Subset Canada Only
Canada <- myDataFull[myDataFull$country=="Canada",]

my_plot <- ggplot(data = Canada, aes(x=year, y=lifeExp))+geom_line()
my_plot

```

```{r working_of knitr, echo=false, results=hide}
### Run this code in R to see graphic of how
### your document gets rendered
```par(mar=rep(0, 4), bty="n", cex=1.5)
plot(0, 0, type="n", xlab="", ylab="", xaxt="n", yaxt="n",
     xlim=c(0, 100), ylim=c(0, 100))
xw <- 10
yh <- 35
xm <- 12
ym <- 50
rect(xm-xw/2, ym-yh/2, xm+xw/2, ym+yh/2, lwd=2)
text(xm, ym, ".Rmd")

xm <- 50
ym <- 80
rect(xm-xw/2, ym-yh/2, xm+xw/2, ym+yh/2, lwd=2)
text(xm, ym, ".md")
xm <- 50; ym <- 25
for(i in c(2, 0, -2))
    rect(xm-xw/2+i, ym-yh/2+i, xm+xw/2+i, ym+yh/2+i, lwd=2,
         border="black", col="white")
text(xm-2, ym-2, "figs/")

xm <- 100-12
ym <- 50
rect(xm-xw/2, ym-yh/2, xm+xw/2, ym+yh/2, lwd=2)
text(xm, ym, ".html")

arrows(22, 50, 38, 50, lwd=2, col="slateblue", len=0.1)
text((22+38)/2, 60, "knitr", col="darkslateblue", cex=1.3)

arrows(62, 50, 78, 50, lwd=2, col="slateblue", len=0.1)
text((62+78)/2, 60, "pandoc", col="darkslateblue", cex=1.3)
```

# InLine Code

The average of the class is 44.0673946. 'r round(44.0673946,2)

'''{r}


